---
title: "Final Project"
author: "Quillo, Carl Louie A."
date: "2023-12-21"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




Select a website that you want to scrape 300 reviews. 
You can select 1 product from Amazon
Or you can select 1 movie
Or you can select reviews from SkyTrax https://www.airlinequality.com/review-pages/a-z-airline-reviews/ ;
the reviews are for the different airlines, but you can only select 1 airline
After scraping 300 reviews, have a basic sentiment analysis with your own analysis and data visualization. each visualization shall have its own description.

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

reviews = data.frame()

for(counterrr in 1:12){
  looplink = paste0("https://www.imdb.com/title/tt1517268/reviews?sort=userRating&dir=desc&ratingFilter=", + counterrr)
  
  link = looplink
  
  session <- bow(link,
               user_agent = "For Educational Purpose")

  
  scrapeNodes <- function(selector){
    scrape(session) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

      rating_name <- scrapeNodes("span.display-name-link")
 

      rating_title <- scrapeNodes("a.title")
      
      
      rating_contents <- scrapeNodes("div.content")
      
      
      rating_date <- scrapeNodes("span.review-date")
      
      
      rating_ratings <- scrapeNodes("div.ipl-ratings-bar")

      reviews <- rbind(reviews, data.frame(name = rating_name,
                      title = rating_title,
                      contents = rating_contents,
                      date = rating_date,
                      ratings = rating_ratings))

}

reviews

```